\documentclass[12pt]{article}         %% What type of document you're writing.


%%%%% Preamble

%% Packages to use
\usepackage[margin=1.1in]{geometry}
\usepackage{amsmath,amsfonts,amssymb}   %% AMS mathematics macros
\usepackage[utf8]{inputenc}
\usepackage{chngcntr}
\usepackage{graphicx}
\counterwithin*{equation}{section}

%% Title Information.

\title{Assignment 2 \\ OCS}
\author{Marko Ivančić \and Mauro Jurada}
\date{11 December 2019}           %% By default, LaTeX uses the current date

%%%%% The Document

\begin{document}

\maketitle

\textbf{Show and describe all your results in the report!}

\section{Size of matrices, number of learnable parameters}
For the Swiss roll dataset at hand, what is the size of the matrices $W^0, W^1$, and the bias terms $b^0$ and $b^1$? Specify the number of learnable parameters of the neural network as a function of $N_H$

\section{Derivative of the total loss}
Compute  the  derivative  of  the  total  loss  w.r.t.   to  all  model  parameters  using  the  results  from  the  practical exercise session.

\section{Initialization of the parameters}
Initialize the parameters using a normal distribution with $\mu= 0 \text{ and } \sigma= 0.05$

\section{Forward pass}
Implement the forward pass of the network.

\section{Backward pass}
Implement the backward pass using the back-propagation algorithm.

\section{Training the neural network}
Train the neural network using the provided training data for 1000 iterations with the steepest descent algorithm for 
$
N_H\in \{4,32,512\}
$.\\
–Select a suitable step size $t^k\in [0.1,0.001] $ and keep it constant over the iterations.\\
–Select the step size with the Armijo rule in each iteration.

\section{Training error vs. accuracy}
Compare the training error and the accuracy of both trainings over the iterations in a plot.  The accuracy is defined as the average number of correctly classified samples

$$
	\mathcal{A} = \dfrac{1}{S}\sum_{n=1}^{S}\delta(y^s,\tilde y^s) \quad\text{with}\; \delta(u, v) = 
	\left\{
	\begin{aligned}
		1 \quad & \text{if } u = v\\
		0 \quad & \text{else,}\\ 
	 \end{aligned} 
	 \right.
$$

where $\delta$ is the indicator function.

\section{Applying the learned network}
Apply the learned network to thetest data and report the loss and the accuracy.

\section{3D scatter plot}
Create  a  3D  scatter  plot  showing  the  samples $x^s$ with  the  true  label $y^s$ and  your  predicted  label $\tilde y^s$ for  the training and test dataset.  Discuss the obtained model performance.

\end{document}

